\section{Numerical validation and systematics}
\label{app:validation}

\subsection{Integrator and conservation}

The relativistic kick--drift--kick leapfrog conserves energy to
$|\Delta E/E|<10^{-4}$ over $10^4$ steps at production timestep
$dt=0.005\fm/c$ in NVE many-body runs, and to $<10^{-6}$ over $2\times
10^4$ steps for an isolated bound two-body orbit; total momentum is
conserved to machine precision.  The energy-shifted cutoff (potential
continuous at $r_{\rm cut}$) eliminates the truncation random walk.
The Maxwell--J\"uttner sampler reproduces the virial estimator
$\Teff=\langle p^2/3E\rangle$ at the half-percent level; free expansion
redshifts momenta exactly as $1/a$.

\subsection{Reaction hazards}

Annihilation is implemented as continuous Poisson hazards, so event
counts are timestep-independent by construction; ensemble survival
probabilities match $e^{-\lambda t/3}$ at the few-percent level for both
the scattering hazard and the bound-pair hazard, and $\tau_{\rm
bound}\to\infty$ recovers immortal bound states exactly.  The
\emph{lifetime calibration} converts the model parameter into an
effective width: a prepared bound meson on a reference orbit spends a
fraction $0.386$ of its period inside $d_{\rm ann}$, and its measured
lifetime is $\tau_{\rm eff}=(7.2\text{--}7.3)\,\tau_{\rm bound}$ across
$\tau_{\rm bound}=0.5$--$2\fm/c$ (150 trials each, exponential MLE),
against the duty-cycle prediction $3/0.386=7.8$.  Four-momentum, color
neutrality, and net flavor are conserved exactly through photon and
re-injection events (asserted at runtime on every event).

\subsection{Cluster identification}

Unit configurations: an $rgb$ triple identifies as one baryon, not
fragments; two well-separated tight mesons never merge into a
tetraquark; a compact $(2,2)$ blob is assigned tetraquark only when its
four-body energy beats every meson+meson split; a $cc\bar u\bar d$
cluster is flagged manifestly exotic while $c\bar c q\bar q$ is not.
The persistence filter (three consecutive snapshots) removes transient
coincidences; its depth, the binding threshold $\Delta E_{\rm th}$, and
the prefilter radius $r_{\rm cl}$ are scanned systematics.

\subsection{Systematics summary}

Table~\ref{tab:syst} varies one knob at a time off the production
baseline ($N=3000$, $H_0=0.1\,c/\fm$, 24 events per variant).

\begin{table}[t]
\caption{Systematics: per-event yields (baryons per species) and the
diquark-first fraction.  Baseline from the 48-event production point.}
\label{tab:syst}
\begin{ruledtabular}
\begin{tabular}{lcccc}
variant & mesons & baryons & tetraquarks & $f_{\rm dq}$ \\
\hline
baseline            & $194.0(1.6)$ & $2.83(19)$ & $0.58(10)$ & $0.95(1)$ \\
$dt/2$              & $194.8(2.4)$ & $2.60(19)$ & $0.54(14)$ & $0.90(3)$ \\
$r_0=0.1\fm$        & $201.7(2.4)$ & $2.48(21)$ & $0.58(15)$ & $0.97(2)$ \\
$r_0=0.3\fm$        & $190.9(2.3)$ & $2.79(22)$ & $0.54(12)$ & $0.92(2)$ \\
persistence 5       & $183.8(2.2)$ & $2.04(20)$ & $0.50(13)$ & $0.95(2)$ \\
$\Delta E_{\rm th}=20\MeV$ & $15.1(8)$ & $0.17(6)$ & $<0.13$ & --- \\
fixed $\lambda_D$   & $6.5(5)$     & $<0.13$    & $<0.13$   & --- \\
\texttt{max\_channel} & $305.4(3.2)$ & $4.56(26)$ & $7.17(65)$ & $0.78(3)$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

Three groups emerge.  \emph{Mild} ($\le5\%$ on yields): timestep,
softening, persistence depth --- genuine numerical systematics.
\emph{Mechanism checks}: freezing $\lambda_D$ (no comoving growth)
nearly extinguishes hadronization ($6.5$ mesons), confirming that the
screening-length growth is the capture engine; and a $20\MeV$ binding
threshold removes $92\%$ of clusters, revealing that Hubble capture
populates predominantly \emph{near-threshold} states --- absolute
yields are threshold-scheme dependent, while ratios move far less
($B/M$: $1.1\%$ vs baseline $1.5\%$).  \emph{Modeling bracket}: the
\texttt{max\_channel} prescription multiplies tetraquark yields by
$12$ and five-quark yields by $\sim10$ at only $1.6\times$ the meson
yield --- the discrete-color prescription is the dominant uncertainty
for exotic ratios and is quoted as a bracket throughout.

Finite size: per-quark meson-bound fractions are $13.1\%$, $12.9\%$,
$13.0\%$ at $N=604$, $3000$, $10^4$, with baryon and tetraquark
per-quark rates scaling within $1\sigma$ across the seventeen-fold
volume change.  \todo{Yukawa-liquid $g(r)$ anchor vs
Ref.~\cite{Hamaguchi:1997pre}.}
