\section{Charge quantization on isolated clusters}
\label{app:charge-quantization}

This appendix establishes the renormalization backbone of Tier~1: that
species labels read from finite-region conserved charges are integers up
to controlled corrections, and that integer labels render species numbers
and their ratios free of anomalous dimensions.

\subsection{Point-split currents (A2)}

For staggered or Wilson quarks the vector currents of flavor $f$ admit
point-split lattice discretizations $j^\mu_f(x)$ that are \emph{exactly}
conserved on the lattice, $\partial^-_\mu j^\mu_f=0$, as operator
identities following from the invariance of the action under local phase
rotations of $\psi_f$.  Exact conservation implies $Z_{j}=1$ to all
orders and vanishing anomalous dimension: the charges built below
renormalize trivially.  The only lattice artifact is a surface ambiguity:
point-split densities straddle links, so a sharp region sum is defined up
to $O(a)$ terms supported on $\partial R$; these are absorbed into the
window-smearing error below.

\subsection{Smeared region charges and the quantization theorem (A1)}

Define the smeared region charge
\begin{equation}
Q^{\ell_w}_{R,f}=\sum_{\mathbf x} f_{R,\ell_w}(\mathbf x)\,
j^0_f(\mathbf x),
\label{eq:qsmear}
\end{equation}
with $f_{R,\ell_w}=1$ deep inside $R$, $0$ far outside, interpolating
smoothly over a shell of width $\ell_w$, $a\ll\ell_w\ll d$.  Sharp
windows ($\ell_w\to0$) develop perimeter-divergent vacuum fluctuations,
$\langle Q_R^2\rangle_c^{\rm vac}\propto|\partial R|/a$ (the
contact-term phenomenon familiar from charge-fluctuation and
symmetry-resolved-entanglement studies); smearing over $\ell_w$ renders
the fluctuations finite, $\langle (Q^{\ell_w}_R)^2\rangle_c^{\rm vac}
= O(|\partial R|\, e^{-m_\pi \ell_w}/\ell_w^2)$ in the gapped theory.

\medskip
\noindent\textbf{Theorem (charge quantization).}
\emph{Let $|\Psi\rangle$ satisfy the cluster condition: there is a region
$R$ with buffer $d$ such that correlations of local operators across the
buffer factorize up to $\epsilon_d = C\,e^{-m_\pi d}$ (cluster
decomposition in a theory with mass gap $m_\pi$), with a state carrying
exact global flavor charge $q\in\mathbb Z$ inside and the vacuum in the
buffer.  Then for $a\ll\ell_w\ll d$ the outcome distribution of a
projective measurement of $Q^{\ell_w}_{R,f}$ obeys}
\begin{equation}
\mathrm{Prob}\Big(\big|Q^{\ell_w}_{R,f}-q\big|>\tfrac12\Big)
\;\le\; C_1\,e^{-m_\pi d}
\;+\; C_2\,\frac{|\partial R|}{\ell_w^2}\,e^{-m_\pi\ell_w}
\;+\; O\!\big((a/\ell_w)^2\big).
\label{eq:quantization}
\end{equation}

\emph{Proof sketch.}  Write $Q^{\ell_w}_{R,f}=Q^{\rm glob}_f-
Q^{\ell_w}_{\bar R,f}$ using exact conservation; $Q^{\rm glob}_f$ is a
superselected integer on $|\Psi\rangle$.  The complement charge acts on
the buffer-and-outside factor, which by the cluster condition is the
vacuum (plus other clusters, themselves integer-charged) up to
$\epsilon_d$; its distribution is then the vacuum distribution of a
smeared charge, whose non-integer spread is bounded by the smeared
vacuum fluctuation above.  Chebyshev on that variance gives the second
term; the $O(a)$ surface ambiguity of the point-split density contributes
at relative order $(a/\ell_w)^2$ after smearing.  \hfill$\square$

\medskip
The measured value is therefore \emph{rounded to the nearest integer}
with exponentially small mislabeling probability: the observable is an
integer label, and integer labels do not run.

\subsection{Gauss-law singlet certification (A3)}

In the Hamiltonian theory the non-Abelian Gauss law equates the total
color charge in $R$ to the chromoelectric flux through $\partial R$:
measuring the boundary-link Casimir $\sum_{\ell\in\partial R}E_\ell^2$
and obtaining vacuum-consistent values certifies, gauge-invariantly and
with the same $e^{-m_\pi d}$ tails, that the cluster in $R$ is a color
singlet.  This certification has no Euclidean analog and is a genuine
capability of real-time Hamiltonian simulation; it converts ``cluster''
from a heuristic into a gauge-invariant statement.

\subsection{RG-safety of species numbers and ratios (D)}

A species assignment built from (i) integer flavor labels
[Eq.~\eqref{eq:quantization}], (ii) the singlet certificate, and (iii)
spectral windows of $H_R$ (Appendix~\ref{app:spectral-projectors}) is a
function of RG-invariant data only.  Consequently the per-event species
multiplicities $N_s$, their ensemble means, and all ratios
$N_s/N_{s'}$ have continuum limits with no anomalous dimensions and no
scheme labels beyond the physically transparent window parameters
$(\ell_{\rm cl},\ell_w,d,t_f)$, each of which comes with a plateau
criterion (Appendix~\ref{app:limits}).  This is the sense in which the
classical ratios of Sec.~\ref{sec:classical-results} acquire a rigorous
QCD counterpart.
