\section{Measurement protocols and systematics budget}
\label{sec:protocols}

Per shot: evolve to $t_f$; locate clusters (front end); certify singlets
(Gauss); measure Tier-1 charges on all clusters; run Tier-2 QPE on
clusters needing spectral identification; record (species, $P^\mu$).
Across shots: species multiplicities, ratios, and Tier-3 pair spectra ---
event-ensemble statistics exactly as in experiment.

\subsection{From shots to ratios}
\label{sec:shots-to-ratios}

The extraction of a \emph{number} $R_{ss'}$ deserves care, because the
per-shot protocol is an \emph{adaptive} measurement chain --- later
measurements act on regions chosen from earlier outcomes --- rather
than the expectation value of any local operator.  Four statements
assemble the ratio:

\emph{(i) The chain is a well-defined quantum instrument.}  Each shot
implements a POVM whose outcome $\omega$ is the list
$\{(s_i,P^\mu_i)\}$ of cluster labels and momenta.  Every primitive in
the chain --- smeared energy density, boundary-flux Casimir, smeared
charges, region-restricted QPE --- is quasi-local, and on cluster
states any pair of primitives with separated or nested supports
commutes up to boundary-supported terms of size $O(e^{-m_\pi d})$
(Appendix~\ref{app:limits}).  The outcome law is therefore independent
of measurement ordering, and back-action within a shot is controlled
by the same exponential that controls every other systematic.  The
region-finding step enters only as classical conditioning and needs no
renormalization of its own.

\emph{(ii) The estimator.}  With $N_s(\omega)=\sum_i
\delta_{s_i s}$, the ratio is estimated as the ratio of shot-averaged
means, $\hat R_{ss'} = \overline{N_s}/\overline{N_{s'}}$, with
standard $O(1/n_{\rm shots})$ ratio-estimator bias and bootstrap
errors --- statistics, not field theory.

\emph{(iii) Unfolding.}  Labels err in enumerable ways: quantization
tails ($e^{-m_\pi d}$), merged clusters (the flagged fraction of
Sec.~\ref{sec:front-end}), and spectral-window collisions.  The
measured count vector is $\langle \mathbf N\rangle_{\rm meas} =
M\,\langle \mathbf N\rangle_{\rm true}$ with $M = \mathbb 1 +
\delta M$, where every entry of $\delta M$ is itself measured (flagged
fractions, window occupancies) or bounded (tails); ratios are quoted
after inverting $M$ --- precisely the efficiency unfolding of an
experimental analysis, with $\delta M \to 0$ in the
plateau/continuum limits.

\emph{(iv) What the ratio means.}  $R_{ss'}$ is not a vacuum constant
of QCD: it is a functional of the specified preparation
$(T, R_F, \mu_B, u^i)$ and of $t_f$ within its plateau --- exactly as
experimental yields are functionals of collision energy and
centrality.  Its field-theoretic content is that this functional has
continuum and infinite-volume limits free of anomalous dimensions
(Appendices~\ref{app:charge-quantization} and \ref{app:limits}),
with all residual scheme dependence confined to stated, scannable
window parameters.  Meaningful comparison is comparison at matched
preparation: to the classical model of
Secs.~\ref{sec:model}--\ref{sec:classical-results} run at the same
$(T, n, H_0)$, to statistical hadronization at the same freeze-out,
and ultimately between simulated and experimental systems of matched
size and energy density.

\todo{systematics table: $\ell_{\rm cl}$- and $d$-plateaus; flagged
merged-cluster fraction; $t_f$-plateau residual slopes per species;
Tier-2 spectral-window collisions; Ward-identity EMT normalization
residuals.}

Statistics are set by the physics, not the protocol: coalescence and
statistical baselines put exotic-to-pion ratios at
$O(10^{-3}$--$10^{-4})$ in heavy-ion conditions
\cite{ExHIC:2010gcb,ExHIC:2017smd,Andronic:2017pug}, and a fireball shot
yields $O(10^2$--$10^3)$ hadrons, so $O(10^2$--$10^4)$ shots give
ten-percent-level exotic yields --- an ensemble-size statement identical
in kind to the event counts of experimental analyses, not an
obstruction.  Two enrichment handles mirror the classical half:
heavy-flavor-biased fireballs (the quantum image of injected $c\bar c$),
and $\mu_B$-biased droplets for the baryon-rich sector.  A third,
practical handle is system size: a pp-scale droplet ($R_F\sim1$--$2\fm$)
needs a far smaller lattice volume than a heavy-ion fireball while the
observable framework is unchanged --- exact event-by-event charge
conservation is automatic in a pure-state simulation, which is precisely
the canonical physics that governs small collision systems
(Sec.~\ref{sec:confrontation}).  The pp-scale quench, not the
heavy-ion one, is therefore the natural first target for hardware.  Our own pilot
classical ensembles illustrate the same accounting from the other side:
180 events resolved tetraquark yields at the few-percent-per-event level
but only bounded pentaquarks, and no $cc\bar q\bar q$ occurred without
enrichment.
